Whole-body connectome of a segmented annelid larva

### 2024-06-16 README.Rmd
README update
Readme: update

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024)
 \. _`r Title`_. Name of journal/book <>

Our pre-print is online here:

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, , Gáspár Jékely, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://zenodo.org/doi/10.5281/zenodo.10825370>

@@

If you would like to use the template, you could open Rstudio in your computer, then go to File > New Project > Version Control > Git. Under repository URL add the URL of this page https://github.com/JekelyLab/Jekely_et_al_2024_connectome and save it in a local folder.

>>>>

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024)
 \. _`r Title`_.  biorxiv. Online at <https://doi.org/10.1101/2024.03.17.585258>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, , Gáspár Jékely, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://zenodo.org/records/11811680>

@@

If you would like to use the template, you could open Rstudio in your computer, then go to File > New Project > Version Control > Git. Under repository URL add the URL of this page https://github.com/JekelyLab/Platynereis_3D_connectome_2024 and save it in a local folder.
